Efficient static analysis of Marlowe contracts

### 2020-05-04 papers/static_analysis2020/paper.tex
Clarify paragraph

One subtle detail that we realised during testing is that, even though
the diagram above shows that a \texttt{When} belongs to the next transaction,
because it will still be there after the previous transaction is executed,
the observations in the \texttt{Notify} cases will correspond to the
\texttt{State} before the \texttt{When} is executed, but to the slot
interval of the transactions that triggers the \texttt{When}. The same
is true for \texttt{Value}s in the \texttt{Deposit} cases, since the amount
to deposit must be calculated without considering the effects of the
deposit itself.

>>>>

One subtle detail that we realised during testing is that, even though
the diagram above shows that a \texttt{When} belongs to the new transaction,
because it will still be there after the previous transaction is executed,
the observations in the \texttt{Notify} cases will correspond to the
information there was in the \texttt{State} before the \texttt{When}
was executed, with the exception of the slot interval, which will still be
considered to be that of the transaction that triggers the \texttt{When} (the
new transaction). The same is true for \texttt{Value}s in the \texttt{Deposit}
cases, since the amount to deposit must be calculated without considering the
effects of the deposit itself, we need to refer to the \texttt{State} before
the deposit was made.
